\chapter{Use Cases Model Survey}
{
    \renewcommand*{\theenumi}{\thesubsection.\arabic{enumi}}
    \renewcommand*{\theenumii}{\theenumi.\arabic{enumii}}
    \renewcommand*{\theenumiii}{\theenumii.\arabic{enumiii}}

    \section{Logging In}
        In this senario the user logs into the system.
        \subsection{Actors}
            \begin{itemize}
                \item User
                \item System
            \end{itemize}
        \subsection{Assumptions}
            \begin{itemize}
                \item User already has valid login information.
                \item User is at the login page.
            \end{itemize}
        \subsection{Procedure}
            \begin{itemize}
                \item System prompts user for login information
                \item User enters correct login information
                \item User clicks ``Login''
                \item The system logs the user in
            \end{itemize}
        \subsection{Expected Outcome}
            \begin{itemize}
                \item The user is now logged in.
            \end{itemize}

    \section{Loggin Out}
        In this senario the user logs out of the system.
        \subsection{Actors}
            \begin{itemize}
                \item User
                \item System
            \end{itemize}
        \subsection{Assumptions}
            \begin{itemize}
                \item User is already logged in
            \end{itemize}
        \subsection{Procedure}
            \begin{itemize}
                \item User clicks the ``Logout'' button
                \item The system logs the user out
                \item The system prompts the user for the login information
            \end{itemize}
        \subsection{Expected Outcome}
            \begin{itemize}
                \item The user is now logged out, redirected to the login page
                and is prompted to login.
            \end{itemize}

    \section{Create a Custom Drink}
        In this scenario the user creates a drink from scratch, selecting 
        what ingredients he wishes to use, as well as their amounts. The 
        user then saves this recipe for future use.
        \subsection{Actors}
            \begin{itemize}
                \item User
                \item System
            \end{itemize}
        \subsection{Assumptions}
            \begin{itemize}
                \item User is already logged in
                \item User is already at the create a draink page
            \end{itemize}
        \subsection{Procedure}
            \begin{itemize}
                \item System presents user with a list of available options to 
                make a drink
                \item User selects which drinks to use
                \item User inputs how much of each ingredient to use
                \item User chooses a name for the new drink
                \item User clicks ``Create Drink''
                \item The system stores the new drink in the database
            \end{itemize}
        \subsection{Expected Outcome}
            \begin{itemize}
                \item The drink is correctly placed into the database for 
                future retrieval.
            \end{itemize}
    
    \section{Create a Drink}
        In this scenario the user selects which premade drink he/she wants 
        DRINC to produce.
        \subsection{Actors}
            \begin{itemize}
                \item User
                \item System
            \end{itemize}
        \subsection{Assumptions}
            \begin{itemize}
                \item User is logged in.
                \item There are valid drinks in the database.
                \item There is a cup in the DRINC machine.
            \end{itemize}
        \subsection{Procedure}
            \begin{itemize}
                \item System prompts user for drink selection
                \item User selects drink
                \item User clicks ``Create''
                \item The system makes the drink and increments the number of
                drinks consumed
                \item User consumes drink
            \end{itemize}
        \subsection{Expected Outcome}
            \begin{itemize}
                \item The drink is created and consumed. User is positively 
                affected by drink.
            \end{itemize}

    \section{Delete a Drink}
        In this scenario the user deletes a drink from the database so that it
        will be removed from the list of valid drinks.
        \subsection{Actors}
            \begin{itemize}
                \item User
                \item System
            \end{itemize}
        \subsection{Assumptions}
            \begin{itemize}
                \item User is logged in.
                \item There is already at least one drink in the database.
            \end{itemize}
        \subsection{Procedure}
            \begin{itemize}
                \item System displays a list of saved drinks
                \item User selects a drink
                \item User clicks ``Delete Drink''
                \item The system pops up with a confirmation ``Are you sure you
                want to delete [Drink x]?''
                \item The user clicks ``Yes'' or ``No''
                \item If the user clicks ``Yes'' the system drops the drink 
                from the database
            \end{itemize}
        \subsection{Expected Outcome}
            \begin{itemize}
                \item The drink is no longer listed under saved drinks.
            \end{itemize}

            
}
