\chapter{Summary of Requirements}
{
    \renewcommand*{\theenumi}{\thesubsection.\arabic{enumi}}
    \renewcommand*{\theenumii}{\theenumi.\arabic{enumii}}
    \renewcommand*{\theenumiii}{\theenumii.\arabic{enumiii}}

    \section{Hardware}
    
    \begin{itemize}
		\item Frame must securely hold 9 liters of mixers, glass enclosures 
        as well as the back end control systems and drink transport track.
		\item Power Supply must be capable of powering the back end control 
        system, drink transport track, valves, and flow meters must be included.
		\item A microcontroller with enough I/O pins to monitor a flow meter 
        and valve for every mixer, as well as the servos controlling the 
        drink transport track and a data connection to the front end system 
        must be used to control the back end control systems
		\item The drink transport track must be able to safely, securely, 
        and accurately move a cup to any point on a square grid.
		\item The transport track requires at least two servos, which must 
        be strong enough to move a full pint of mixed drink reliably.
		\item Each mixer must have a valve that can be quickly turned on and 
        off via the back end control system.
    \end{itemize}

    \section{Software}

    \begin{itemize}
		\item The website must be able to log in a user based off of 
        authentication held in the backend database.
		\item The website must be able to log a user off of the account.
		\item The website must present the user with the main menu upon 
        logging in
		\item The website must have the following options:
        \begin{itemize}
			\item Create a Custom Drink
			\item Select a Drink
			\item Most Drank
        \end{itemize}
		\item The Android app must be able to log in a user based off of 
        authentication held in the backend database.
		\item The Android app must be able to log a user off of the account.
		\item The Android app must present the user with the main menu upon 
        logging in
		\item The Android app must have the following options:
        \begin{itemize}
			\item Create a Custom Drink
			\item Select a Drink
			\item Most Drank
        \end{itemize}
    \end{itemize}

    The goal of this project is to create a machine that will accurately mix 
    drinks selected by the user from a preset list of mixers.  

}
